\bf Faster Neural Machine Translation Inference

### 2018-05-11 fast-beam/fast-beam.tex
use requireProb

In fact, we are usually only interested in the best class during inference, not the probability. Since we now compute the best class before the softmax, we can skip softmax altogether, Algorithm~\ref{algo:Argmax only}. This is only possible for beam size 1; the comparison between softmax probabilities is required for larger beam sizes as the denominators are different for different hypotheses.

>>>>

Thirdly, calculation of $max$ and $sum$ can be done in one loop by adjusting the sum whenever a higher $max$ is found, Equation~`.
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $\Delta = max_b - max_a$ and $max_b > max_a$.

In fact, a well known optimization is to skip the softmax operation altogether and calculate the argmax over the input vector, Algorithm~\ref{algo:Argmax only}. This is only possible for beam size 1 and when we are not interested in returning the softmax probabilities.
